Identification and analysis of pleiotropic expression quantitative trait loci

### 2023-05-10 doc/presentation_230511_centuriday2023/presentation_centuri2023_marseille.tex
DOC centuri

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Annotation of eQTLs traits using colocalization analysis}

        \begin{center}
            \includegraphics[width=0.6\textwidth]{\presentationgoldparispath/doi_10.3389_fgene.2020.00424_fig4bc.png}
        \end{center}

@@

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        \end{center}
        \vfill
        Yes, number of target gene increaseas with the pleiotropy

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Genetic variants with effect on trait and gene expression}

        Colocalization of eQTLs and GWAS variants

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\presentationgoldparispath/doi_10.3389_fgene.2020.00424_fig4bc.png}
        \end{center}

@@

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        \end{center}
        \vfill
        Yes, number of target gene increases with the pleiotropy

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Applications / Collaborations}

        \begin{itemize}
            \item Dataset of traits, categories, tissues and cell types
            \item Annotation of genomic regions
            \item Annotation of genes
        \end{itemize}
